Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-21 paper/paper.tex
fixed paragraph breaks
systems engineering from adrien-needs work, will fix tonight

We need to give an overview of our airframe, autopilot, and payload requirments. Amanda or Anthony should decide how to proceed here based on other good papers.

One thing we need is a good justification for having built two fucking giant airframes. Lets point out that we initially assumed a much heavier payload, but found lighter and smaller alternatives as the year went on. We decided it was better to be too big than too small. A large plane with lower wing loading would be easier to control, and easier to recover in case power is lost. (someone check that math)

>>>>

The main systems engineering approach that was used in order to finish construction of the planes efficiently and in a timely manner was to break the team into two main groups: the mechanical team and the electronics team.  The mechanical team was in charge of the rebuild and build process of the \emph{Daedalus} and the \emph{Knight Two}, respectively.  In order to maximize efficiency we further divided the mechanical team into sub groups placing members where they were best suited.  During both constructions we split into a wing and tail section group and a fuselage group.  While all the construction was going on, two expert builders from the local R/C club would come and advise us when we were unsure how to proceed in order to have the best balance of weight and strength.  Along with the actual construction of the planes, the mechanical team also focused on modifying the structures of the planes in order to fit the desired payload: the autopilot system and the imaging system.

The electronics team was in charge of the autopilot system and the imaging system.  Originally a large and heavy system was to be used for an imaging system, but as the year progress a lighter and smaller alternative was found, which helped the mechanical team in the placement of the imaging system…(I do not know the details of what they did, that’s all Pat)

We will be performing a manual take off, and giving the autopilot system control of the aircraft once the plane is in the air.  For landing, we will do the same process in reverse, and land the plane manually.

%One thing we need is a good justification for having built two fucking giant airframes. Lets point out that we initially assumed a much heavier payload, but found lighter and smaller alternatives as the year went on. We decided it was better to be too big than too small. A large plane with lower wing loading would be easier to control, and easier to recover in case power is lost. (someone check that math)
